Airspace configuration with Monte Carlo tree search

### 2018-01-24 article/prework.tex
(+) added algorithms

\documentclass{article}
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}

@@

\section{Preliminaries}
\subsection{Base theory: the environment and notations}
Notations based on Markov Decision Problem's theory (taken
from~\cite{browne2012survey})
\begin{itemize}
  \item \(S\) a set of states,
  \item \(\mathcal{A}\) a set of actions,
  \item \(T(s, a, s')\) a transition model that determines the probability of
      reaching state \(s'\) if action \(a\) is applied to state \(s\),
  \item \(R(s)\) a reward function
\end{itemize}

@@

\subsection{Monte Carlo tree search}
In the MCTS, the action \(a\) is the path that leads from the root the the best
node computed so far

\bibliography{article}
\bibliographystyle{plain}
\end{document}

>>>>

\documentclass{article}
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}

@@

\section{Preliminaries}
\subsection{Base theory: the environment and notations}
Notations based on Markov Decision Problem's theory (taken
from~\cite{browne2012survey})
\begin{itemize}
  \item \(\mathcal{S}\) a set of states,
  \item \(\mathcal{A}\) a set of actions,
  \item \(T(s, a, s')\) a transition model that determines the probability of
      reaching state \(s'\) if action \(a\) is applied to state \(s\),
  \item \(R(s)\) a reward function
\end{itemize}

A policy is a mapping \(\pi \colon \mathcal{S} \to \mathcal{A}\). The aim is to
output, from a state \(s\), the action that gives the highest reward.

@@

\subsection{Bandits methods}

\subsection{Monte Carlo tree search}
In the MCTS, the action \(a\) is the path that leads from the root to the best
node computed so far. To each node should correspond a state \(s\). This way, an
action \(a\) from a node with state \(s\) gives an other node with an other
state \(s'\).

\bibliography{article}
\bibliographystyle{plain}

\section{Algorithms}
\subsection{Monte carlo}
\begin{algorithm}
  \caption{General MCTS approach~\cite{browne2012survey}}
  \begin{algorithmic}
    \Function{MctsSearch}{$s_0$}
    \State{}create root node \(v_0\) with state \(s_0\)
    \While{within computational budget}
    \State{} \(v_l \gets\) \Call{TreePolicy}{$v_0$}
    \State{} \(\Delta \gets\) \Call{DefaultPolicy}{$s(v_l)$}
    \State{} \Call{Backup}{$v_l$, $\Delta$}
    \EndWhile{}
    \Return{\(a(\)\Call{BestChild}{$v_0$}\()\)}
    \EndFunction{}
  \end{algorithmic}
\end{algorithm}
\end{document}
